### 2016-11-15 Writing/draft.tex
Added references and updated structure

Discrete characters correlation have been studied in the context of Phylogenetic Comparative Methods to test whether two or more characters could have coevolved (Maddison 1990, Evolution; Pagel 1994, Proc B).
However, nobody (that we know of) has looked at what is the effect of actually coding characters that coevolved in a phylogenetic matrix.

-Morphological characters are more and more used: phenomics, tip-dating, Total-Evidence.

-More accurate methods (parsimony vs Bayesian) and better models (Mk, Mk variable from Wright).

-But question remains on which characters to code!

-Don't code correlated characters but what is the actual effect of that? And how many characters are ``secretly'' correlated?

\cite{Davalos01072014}: character correlation + signal in bats
\cite{Grabowski2016}: amount of data needed for testing correlations? CHECK
\cite{Lande1983}: measure correlation CHECK
\cite{Pagel1994}: measure correlation
\cite{Pagel2006}: measure correlation Bayesian
\cite{Maddison1990}: measure binary state character correlation for testing coevol

@@

We define characters as being correlated if they give the same phylogenetic information.

@@

In order to measure, the difference between two characters, we propose a new distance metric defined as follows:

@@

@@

@@

>>>>

The last five years have seen a drastic expansion (resurgence?) of the use of discrete morphological data in macroevolutionary studies.
In fact, traditionally confined to classic cladistics \citep{felsenstein2004inferring} these methods have recently been highly improved whether based on the models and methods for inferring phylogenies (\citealt{lewisa2001} + BAPSTinReview; with some debate on which method to use: \citealt{spencerefficacy2013,wrightbayesian2014,OReilly20160081}) or the methods to date them \citep[e.g.][]{bapsta2013} or to combine them with molecular data \citep{pyrondivergence2011,ronquista2012}.
In parallel, much development has also been done on pre-phylogenetic analysis \citep[e.g. data collection;][]{morphobank} as well as on post-phylogenetic analysis \citep[e.g. morphological disparity analysis;][]{Close2015,Claddis}.

However, using discrete morphological data comes with several caveats, like the effect of missing data \citep{Guillerme2016146} or of the model \citep{OReilly20160081}.
One specific assumption is that coded characters should not be correlated \citep{Brazeau2011}[FIND BETTER CITE?].

Character correlation can be due to
- co-evolution of two traits (e.g. the character ``number of digits on a limb'' co-evolves with the character ``presence/absence of limb'' - this correlation can be sometimes fairly obvious, sometimes less)
- modularity of morphological features [CITE GOSWAMI!]
- convergent evolution (e.g. the character ``flight'') [???]
- error from the coder (e.g. a coder can unintentionally code the same feature multiple times, thus effectively waiting it, for example: ``presence/absence of a proximal end on a limb'' and ``presence/absence of a distal end on a limb'' - effectively weighting the character ``presence/absence of a limb'' by two).
%-Don't code correlated characters but what is the actual effect of that? And how many characters are ``secretly'' correlated?

A lot of work has been done on character correlation \textit{per se}, but focussing mainly on how to measure correlation between characters to detect patterns of coevolution \citep{Lande1983,Maddison1990,Pagel1994,Pagel2006,Grabowski2016}.
However, only several attempts have been made on the actual effect of characters correlation on phylogenetic inference with two notable expections of \cite{Davalos01072014} on empirical data and \cite{ZouConvergence} on molecular data.
It is thus still unclear what will be the effect of characters correlation on phylogenetic inference.

% \cite{Davalos01072014}: character correlation + signal in bats
% \cite{Grabowski2016}: amount of data needed for testing correlations? CHECK
% \cite{Lande1983}: measure correlation CHECK
% \cite{Pagel1994}: measure correlation
% \cite{Pagel2006}: measure correlation Bayesian
% \cite{Maddison1990}: measure binary state character correlation for testing coevol
% \cite{ZouConvergence}: convergence measured as characters correlation (Removing convergence prone characters improves accuracy)

In this study, we propose a new way to measure character correlation (more adapted to discrete morphological characters) and test on simulated and empirical data what is the effect of character correlation on topology. %TG: check if we do just topology?
In other words, we generate matrices and maximise or minimise character correlation and see how that affects topology.

@@

@@

We define characters as being correlated if they give the same phylogenetic information.
In order to measure, the difference between two characters, we propose a new distance metric defined as follows:

@@

We simulated discrete morphological matrices based on the \texttt{dispRity R} package \citep[][; \url{https://github.com/TGuillerme/dispRity}]{thomas_guillerme_2016_55646}.

@@

We applied the same procedure described above to 100 empirical matrices downloaded from TreeBASE (\url{http://treebase.org/}).
The 100 matrices where selected to be the most representative of empirical work with discrete morphological data: with randomly selected matrices with more than 100 each, published between 1985 and 2013 and covering 19 taxonomic classes within 6 phyla (Chordata, Arthropoda, Annelida, Angiosperm, Gymnosperm and Pteridophyta).
The full list of matrices is available in the supplementary materials @@@.

@@

\section{Results}

\section{Discussion}

\subsection{Conclusion}
